---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AUCtrap: AUC calculation using the trapezoidal rule

The goal of the `AUCtrap` package is to provide utilities for calculating the area under the curve for longitudinal measurements.

## Installation

You can install the development version of AUCtrap from  [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("anikoszabo/AUCtrap")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AUCtrap)
AUCtrap(0:3, c(3,4,1,2))
AUCtrap(0:3, c(3,4,1,2), method="iAUC")
```

A formula can be used:

```{r flaexample}
dd <- data.frame(Time = 0:4, Value = c(3,4,1,2,10))
AUCtrap(Value ~ Time, data=dd)

ex2 <- AUCtrap(0:3, c(3,4,1,2), method="iAUC")
ex2
plot(ex2)

```
